02_DESeq2

### 2020-05-06 analysis/02_DESeq2.Rmd
now with tissue specific degs

```{r}

for(i in "gonad"){

@@

>>>>

```{r eval = F}

## first or sex

for(i in levels(colData$tissue)){

@@

## then for tissue

dds <- DESeqDataSetFromMatrix(countData = countData,
                                colData = colData,
                                design = ~ tissue )
dds <- dds[rowSums(counts(dds) > 1) >= 10]  # filter more than sample with less 0 counts
print(dds)
print(dim(dds))
dds <- DESeq(dds, parallel = TRUE) # Differential expression analysis

vsd <- as.data.frame(assay(vst(dds, blind=FALSE)))
write.csv(vsd, "../results/DEseq2/tissue/tissuevsds.csv")
print(head(vsd))

# save differential gene expression results
HP <- createDEGdfsavestissue("pituitary", "hypothalamus")
HG <- createDEGdfsavestissue("gonad", "hypothalamus")
PG <- createDEGdfsavestissue("gonad", "pituitary")
